Ricci-Ollivier Curvature of the Rooted Phylogenetic Subtree-Prune-Regraft Graph

### 2015-07-27 curvature.tex
minor fix to make a proof more standalone. removed extra braces from the table changes

\begin{table}
\centering
\caption{p-values for ordinary least squares linear multiple regression of rSPR mean access time against degree and distance (two-tailed $t$-test of regression coefficient). The p-values for 7 taxa are smaller than the machine precision used to calculate them.}
\csvautotabular{tables/mean-access.csv}}
\label{tab:regressionMAT}
\end{table}

@@

\begin{table}
\centering
\caption{p-values for ordinary least squares linear multiple regression of rSPR $\delta_1$ against degree, distance, and $\kappa$ (two-tailed $t$-test of regression coefficient).}
\csvautotabular{tables/delta1.csv}}
\label{tab:regressionDelta}
\end{table}

@@

\computedegree*
\begin{proof}
	The statement follows if each of the neighbor assignments are disjoint, that is $N(T,u) \cap N(T,v) = \emptyset$, for all nodes $u$, $v$ of $T$.
	So, suppose, for the purpose of obtaining a contradiction, that there exist two nodes $u$ and $v$ of $T$ such that there exists a tree $S \in (N(T,u) \cap N(T,v))$.
	Then $S$ can be obtained from $T$ by moving the subtrees rooted at $u$ or $v$.
	Call these $U$ and $V$, respectively.
	This implies that both $T \setminus U = S \setminus U$ and $T \setminus V = S \setminus V$ by the definition of an rSPR operation.
	Then the rSPR moves that move $U$ or $V$ to obtain $S$ must be nearest neighbor interchanges (NNIs), that is, rSPR moves which move their subtree to one of four locations: their grandparent edge, aunt edge, sibling's left child edge or sibling's right child edge.
	This implies that, without loss of generality, $U$ is moved to its grandparent edge and $V$ to $U's$ sibling (i.e. (iii) above) or $U$ is moved to its aunt edge and $V$ to $U$'s edge (i.e. (iv) above), a contradiction.
	Therefore the claim holds.
\end{proof}

>>>>

\begin{table}
\centering
\caption{p-values for ordinary least squares linear multiple regression of rSPR mean access time against degree and distance (two-tailed $t$-test of regression coefficient). The p-values for 7 taxa are smaller than the machine precision used to calculate them.}
\csvautotabular{tables/mean-access.csv}
\label{tab:regressionMAT}
\end{table}

@@

\begin{table}
\centering
\caption{p-values for ordinary least squares linear multiple regression of rSPR $\delta_1$ against degree, distance, and $\kappa$ (two-tailed $t$-test of regression coefficient).}
\csvautotabular{tables/delta1.csv}
\label{tab:regressionDelta}
\end{table}

@@

\computedegree*
\begin{proof}
	The statement follows if each of the neighbor assignments are disjoint, that is $N(T,u) \cap N(T,v) = \emptyset$, for all nodes $u$, $v$ of $T$.
	So, suppose, for the purpose of obtaining a contradiction, that there exist two nodes $u$ and $v$ of $T$ such that there exists a tree $S \in (N(T,u) \cap N(T,v))$.
	Then $S$ can be obtained from $T$ by moving the subtrees rooted at $u$ or $v$.
	Call these $U$ and $V$, respectively.
	This implies that both $T \setminus U = S \setminus U$ and $T \setminus V = S \setminus V$ by the definition of an rSPR operation.
	Then the rSPR moves that move $U$ or $V$ to obtain $S$ must be nearest neighbor interchanges (NNIs), that is, rSPR moves which move their subtree to one of four locations: their grandparent edge, aunt edge, sibling's left child edge or sibling's right child edge.
	This implies that, without loss of generality, $U$ is moved to its grandparent edge and $V$ to $U's$ sibling (move type (iii)) or $U$ is moved to its aunt edge and $V$ to $U$'s edge (move type (iv)), a contradiction.
	Therefore the claim holds.
\end{proof}
